Red Wine Exploration by Prabhpreet Sandhu
========================================================

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}

library(ggplot2)
library(gridExtra)
library(GGally)
library(dplyr)
library(memisc)
```

```{r echo=FALSE, Load_the_Data}
# Load the Data
rw <- read.csv('wineQualityReds.csv')
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
str(rw)
summary(rw)
```

This report explores the Red Wine dataset containing 12 properties of the wine.

```{r echo=FALSE, message=FALSE, warning=FALSE}
rw$quality.factor <- factor(rw$quality)

rw$quality.category <- ifelse(rw$quality >= 7, 'good', ifelse((rw$quality <= 6) 
                              & (rw$quality) > 4, 'medium', 'bad'))


rw$quality.category <- factor(rw$quality.category, levels = c("bad", "medium", 
                                                              "good"))

```

Quality is numeric variable. Converting it to factor variable for analysis and 
adding a new variable to the dataset.

# Univariate Plots Section

Univariate plots to understand which variables are normal or 
close to normal distribution.

```{r echo=FALSE, message=FALSE, warning=FALSE, Univariate_Plots}
# Histogram is right skewed (normally distributed)
h1 <- ggplot(data = rw, aes(x = fixed.acidity)) +
  geom_histogram(binwidth = 0.1) +
  ggtitle("Fixed Acidity Histogram")

# Here data is right skewed with 3 peaks between 0.4-0.6 
#(close to normal distribution)
h2 <- ggplot(data = rw, aes(x = volatile.acidity)) +
  geom_histogram(binwidth = 0.01) +
  ggtitle("Volatile Acidity Histogram")


# it is normally distributed 
h5 <- ggplot(data = rw, aes(x = density)) +
  geom_histogram() +
  ggtitle("Density Histogram")

# close to normal distribution
h6 <- ggplot(data = rw, aes(x = pH)) +
  geom_histogram() +
  ggtitle("pH Histogram")

# close to normal distribution
h8 <- ggplot(data = rw, aes(x = alcohol)) +
  geom_histogram(binwidth = 0.1) +
  ggtitle("Alcohol Histogram")

# normally distributed
h12 <- ggplot(data = rw, aes(x = quality)) +
  geom_histogram()

grid.arrange(h1, h2, h5, h6, h8, h12, ncol = 2)
```

All there variables are normally or close to normal distriburion.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Histogram has long tail, with a peak at 2 
#(is not or close to normal distribution)
h3 <- ggplot(data = rw, aes(x = residual.sugar)) +
  geom_histogram(binwidth = 0.1) +
  ggtitle("Residual Sugar Histogram")

# right skewed with outliers, not normally distrbuted
h4 <- ggplot(data = rw, aes(x = chlorides)) +
  geom_histogram(binwidth = 0.01) +
  ggtitle("Chlorides Histogram")

# not normally distributed with data right skewed
h7 <- ggplot(data = rw, aes(x = sulphates)) +
  geom_histogram(binwidth = 0.01) +
  ggtitle("Sulphates Histogram")

# not normally distributed
h9 <- ggplot(data = rw, aes(x = citric.acid)) +
  geom_histogram(binwidth = 0.01) +
  ggtitle("Citric Acid Histogram")

# not normally distributed, data right skewed
h10 <- ggplot(data = rw, aes(x = free.sulfur.dioxide)) +
  geom_histogram(binwidth = 1) +
  ggtitle("Free Sulfur Dioxide Histogram")

# not normally distrbuted, data right skewed
h11 <- ggplot(data = rw, aes(x = total.sulfur.dioxide)) +
  geom_histogram(binwidth = 1) +
  ggtitle("Total Sulfur Dioxide Histogram")

grid.arrange(h3, h4, h7, h9, h10, h11, ncol = 2)
```

All these variables are not normally distributed.

```{r echo=FALSE, message=FALSE, warning=FALSE, Bar_Chart}
# bar plot for quality.category(new variable) to see the distribution of wines
b1 <- ggplot(data = rw, aes(x = quality.category)) +
  geom_bar() +
  ggtitle("Bar Chart For Wine Category")

grid.arrange(b1)
```

Bar Chart for qulity.category (new column added)

```{r echo=FALSE, message=FALSE, warning=FALSE}
# transforming data, takin log10
ht1 <- ggplot(data = rw, aes(x = residual.sugar)) +
  geom_histogram(binwidth = 0.05) +
  ggtitle("Residual Sugar Histogram") +
  scale_x_log10()

# transforming data, log10
ht2 <- ggplot(data = rw, aes(x = chlorides)) +  
  geom_histogram(binwidth = 0.05) +
  ggtitle("Chlorides Histogram") +
  scale_x_log10()

# transforming data, log10
ht3 <- ggplot(data = rw, aes(x = sulphates)) +
  geom_histogram(binwidth = 0.01) +
  ggtitle("Sulphates Histogram") +
  scale_x_log10()

# transforming data, taking log10
ht4 <- ggplot(data = rw, aes(x = free.sulfur.dioxide)) +
  geom_histogram(binwidth = 0.1) +
  ggtitle("Free Sulfur Dioxide Histogram") +
  scale_x_log10()

# not normally distrbuted, data right skewed
ht5 <- ggplot(data = rw, aes(x = total.sulfur.dioxide)) +
  geom_histogram(binwidth = 0.1) +
  ggtitle("Total Sulfur Dioxide Histogram") +
  scale_x_log10()


grid.arrange(ht1, ht2, ht3, ht4, ht5, ncol = 2)

```

Data Transformations for properties which are not normally distributed

# Univariate Analysis

### What is the structure of your dataset?

There are 1599 observations, and 11 properties of the wine. Then I converted 
quality variable to factor variable, and added a new column to the dataset. 
And then added 1 more column quality.category to the dataset. 
Observations:
1. Most of the red wine quality rating is 5/6.
2. Maximum wine quality dataset belongs to medium after categorising the 
wine quality.
3. Limited Data for other qualities.
4. Red Wine properties: fixed.acidity, volatile.acidity, density, pH, alcohol 
are close to normal distribution.
5. Red Wine properties: residual.sugar, chlorides, sulphates, citric.acid, 
free.sulfur.dioxide, total.sulfur.dioxide are not normally distributed.


### What is/are the main feature(s) of interest in your dataset?

To investigate what properties of the wine affects the rating of the wine.

### What other features in the dataset do you think will help support your \

Features like pH, alcohol, sulphates, chorides will help.

### Did you create any new variables from existing variables in the dataset?

Converted numeric variable quality to factor variable and assigned this new 
variable to qualilty.factor. 
And added quality.category variable to the dataset, based on the quality rating. 
(1-3 -> bad, 4-6 -> medium, 7-10 -> good)

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?

residual.sugar, chlorides, sulphates, citric.acid, free.sulfur.dioxide, 
total.sulfur.dioxide are not normal or close to normal distribution. Converted 
these variables taking log10 to make them close to normal distribution.

# Bivariate Plots Section

```{r echo=FALSE, message=FALSE, warning=FALSE, Bivariate_Plots}
ggpairs(rw, title = "Red Wine Properties Dataset plots", columns = 2:13)

```

```{r echo=FALSE, message=FALSE, warning=FALSE}
bp1 <- ggplot(data = rw, aes(x = quality.category, y = fixed.acidity)) +
  geom_jitter(alpha = 0.3) +
  geom_boxplot(alpha = 0.5) +
  coord_cartesian(ylim = c(4, 14)) +
  stat_summary(fun.y = "mean", geom = "point", color = "red", shape = 8, 
               size = 4)

bp3 <- ggplot(data = rw, aes(x = quality.category, y = citric.acid, 
                             fill = quality.category)) +
  geom_jitter(alpha = 0.3) +
  geom_boxplot(alpha = 0.5) +
  coord_cartesian(ylim = c(0.00, 0.75)) +
  ggtitle('Citric Acid Boxplot') +
  xlab('Quality Category') +
  ylab('Citric Acid') +
  scale_fill_manual(breaks = c("bad", "medium", "good"), values = 
                      c("red", "yellow", "green")) +
  stat_summary(fun.y = "mean", geom = "point", color = "red", shape = 8, 
               size = 4)

bp10 <- ggplot(data = rw, aes(x = quality.category, y = alcohol)) +
  geom_jitter(alpha = 0.3) +
  geom_boxplot(alpha = 0.5) +
  coord_cartesian(ylim = c(8, 14)) +
  scale_fill_manual(breaks = c("bad", "medium", "good"), values = 
                      c("red", "yellow", "green")) +
  stat_summary(fun.y = "mean", geom = "point", color = "red", shape = 8, 
               size = 4)

bp11 <- ggplot(data = rw, aes(x = quality.category, y = sulphates)) +
  geom_jitter(alpha = 0.3) +
  geom_boxplot(alpha = 0.5) +
  coord_cartesian(ylim = c(0.0, 1.25)) +
  stat_summary(fun.y = "mean", geom = "point", color = "red", shape = 8, 
               size = 4)

grid.arrange(bp1, bp3, bp10, bp11, ncol = 2)
```

Looking at these box plots, as the quantity increases better the rating of 
the wine.

```{r echo=FALSE, message=FALSE, warning=FALSE}
bp2 <- ggplot(data = rw, aes(x = quality.category, y = volatile.acidity)) +
  geom_jitter(alpha = 0.3) +
  geom_boxplot(alpha = 0.5) +
  coord_cartesian(ylim = c(0.2, 1.2)) +
  stat_summary(fun.y = "mean", geom = "point", color = "red", shape = 8, 
               size = 4)  

bp5 <- ggplot(data = rw, aes(x = quality.category, y = chlorides)) +
  geom_jitter(alpha = 0.3) +
  geom_boxplot(alpha = 0.5) +
  coord_cartesian(ylim = c(0.0, 0.2)) +
  stat_summary(fun.y = "mean", geom = "point", color = "red", shape = 8, 
               size = 4)  

bp9 <- ggplot(data = rw, aes(x = quality.category, y = pH)) +
  geom_jitter(alpha = 0.3) +
  geom_boxplot(alpha = 0.5) +
  coord_cartesian(ylim = c(2.5, 4)) +
  stat_summary(fun.y = "mean", geom = "point", color = "red", shape = 8, 
               size = 4)  
  

grid.arrange(bp2, bp5, bp9, ncol = 1)
```

Looking at these Box Plots, we can say that as the quantity decreases, 
the quality rating gets better for Red wine.

```{r echo=FALSE, message=FALSE, warning=FALSE}
bp4 <- ggplot(data = rw, aes(x = quality.category, y = residual.sugar)) +
  geom_jitter(alpha = 0.3) +
  geom_boxplot(alpha = 0.5) +
  coord_cartesian(ylim = c(1, 5)) +
  stat_summary(fun.y = "mean", geom = "point", color = "red", shape = 8, 
               size = 4)  
  
bp6 <- ggplot(data = rw, aes(x = quality.category, y = free.sulfur.dioxide)) +
  geom_jitter(alpha = 0.3) +
  geom_boxplot(alpha = 0.3) +
  coord_cartesian(ylim = c(0, 30)) +
  stat_summary(fun.y = "mean", geom = "point", color = "red", shape = 8, 
               size = 4)

bp7 <- ggplot(data = rw, aes(x = quality.category, y = total.sulfur.dioxide)) +
  geom_jitter(alpha = 0.3) +
  geom_boxplot(alpha = 0.3) +
  coord_cartesian(ylim = c(0, 80)) +
  stat_summary(fun.y = "mean", geom = "point", color = "red", shape = 8, 
               size = 4)

bp8 <- ggplot(data = rw, aes(x = quality.category, y = density)) +
  geom_jitter(alpha = 0.3) +
  geom_boxplot(alpha = 0.3) +
  coord_cartesian(ylim = c(0.990, 1.003)) +
  stat_summary(fun.y = "mean", geom = "point", color = "red", shape = 8, 
            size = 4)

grid.arrange(bp4, bp6, bp7, bp8, ncol = 2)

```

These properties doesn't seem to have any effect on the quality rating 
of the wine.

```{r echo=FALSE, message=FALSE, warning=FALSE}
n1 <- ggplot(data = rw, aes(x = citric.acid, y = pH)) +
  geom_point(alpha = 0.1) +
  geom_smooth(method = 'lm')

n2 <- ggplot(data = rw, aes(x = fixed.acidity, y = pH)) +
  geom_point(alpha = 0.1) +
  geom_smooth(method = 'lm')

n3 <- ggplot(data = rw, aes(x = density, y = pH)) +
  geom_point(alpha = 0.1) +
  geom_smooth(method = 'lm')

n4 <- ggplot(data = rw, aes(x = volatile.acidity, y = citric.acid)) +
  geom_point(alpha = 0.1) +
  geom_smooth(method = 'lm')

n5 <- ggplot(data = rw, aes(x = density, y = alcohol)) +
  geom_point(alpha = 0.1) +
  coord_trans(y = 'log10') +
  geom_smooth(method = 'lm')

grid.arrange(n1, n2, n3, n4, n5, ncol = 2)

```

These variables have negative correlations with each other. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
p1 <- ggplot(data = rw, aes(x = volatile.acidity, y = pH)) +
  geom_point(alpha = 0.1) +
  geom_smooth(method = 'lm')

p2 <- ggplot(data = rw, aes(x = fixed.acidity, y = citric.acid)) +
  geom_point(alpha = 0.1) +
  geom_smooth(method = 'lm')

p3 <- ggplot(data = rw, aes(x = fixed.acidity, y = density)) +
  geom_point(alpha = 0.1) +
  geom_smooth(method = 'lm')

p4 <- ggplot(data = rw, aes(x = citric.acid, y = density)) +
  geom_point(alpha = 0.1) +
  geom_smooth(method = 'lm')

p5 <- ggplot(data = rw, aes(x = log10(total.sulfur.dioxide), 
                            y = log10(free.sulfur.dioxide))) +
  geom_point(alpha = 0.1) +
  geom_smooth(method = 'lm')


grid.arrange(p1, p2, p3, p4, p5, ncol = 2)
```

These variable have positive correlation.

# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?
Positive corelations among variables
1. fixed.acidity & density
2. fixed.acidity & citric.acid
3. pH & volatile.acidity

Negative correlation
1. pH & fixed.acidity
2. pH & citric.acid
3. pH & density
4. citric.acid & volatile.acidity
5. alcohol & density


### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?
There's a strong positive correlation between total.sulfur.dioxide 
& free.sulfur.dioxide.

### What was the strongest relationship you found?
Strongest positive correlation is between 
1. fixed.acidity & citric.acid
2. fixed.acidity & density
3. total.sulfur.dioxide & free.sulfur.dioxide 

# Multivariate Plots Section

```{r echo=FALSE, message=FALSE, warning=FALSE}
'my_data <- select(rw, fixed.acidity, volatile.acidity, citric.acid, 
                  residual.sugar, chlorides, free.sulfur.dioxide, 
                  total.sulfur.dioxide, density, pH, sulphates, alcohol, 
                  quality)

cor_1 <- cor(my_data)'
ggcorr(rw[, 2:13], label = TRUE, nbreaks = 4, method = c("all.obs", "spearman"),
       name = "spearman correlation coefficient", hjust=0.8, angle=-70, size=4) +
  ggtitle('Spearman Correlation Coefficient Matrix')
```

Now before proceeding to multivariate plots, looking at the matrix of 
correlation coefficient of all the properties with quality, following have 
strong positive correlation with quality
1. fixed.acidity
2. citric.acid
3. sulphates
4. alcohol

These were the outcome of the boxplot as well.
Now let's concentrate on the main 4 chemical properties of red wine, which were 
outcome of bivariate analysis & correlation matrix.

```{r echo=FALSE, message=FALSE, warning=FALSE, Multivariate_Plots}
mp1 <- ggplot(data = rw, aes(x = alcohol, y = citric.acid, 
                             color = quality.factor)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = 'lm', se = FALSE, fill = NA) +
  scale_x_continuous(limits = c(quantile(rw$alcohol, probs = 0.01), 
                                quantile(rw$alcohol, probs = 0.99))) +
  scale_y_continuous(limits = c(quantile(rw$citric.acid, 
                                         probs = 0.01), 
                                quantile(rw$citric.acid, 
                                         probs = 0.95))) +
  scale_color_brewer(palette = "Blues") +
  ggtitle("Wine Quality by alcohol vs citric acid")

grid.arrange(mp1, ncol = 1)
```

High alcohol & high level of citric.acid produces better quality wines.

```{r echo=FALSE, message=FALSE, warning=FALSE}
mp2 <- ggplot(data = rw, aes(x = fixed.acidity, y = density, 
                             color = quality.factor)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = 'lm', se = FALSE, fill = NA) +
  scale_x_continuous(limits = c(quantile(rw$fixed.acidity, probs = 0.01), 
                                quantile(rw$fixed.acidity, probs = 0.99))) +
  scale_y_continuous(limits = c(quantile(rw$density, probs = 0.01), 
                                quantile(rw$density, probs = 0.99))) +
  scale_color_brewer(type = 'seq', guide = guide_legend(title = 'Quality')) +
  ggtitle("Wine Quality by fixed.acidity vs density")

grid.arrange(mp2, ncol = 1)
```

Low Density wines & High fixed.acidity are better wine quality.

```{r echo=FALSE, message=FALSE, warning=FALSE}
mp3 <- ggplot(data = rw, aes(x = pH, y = volatile.acidity, 
                             color = quality.factor)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = 'lm', se = FALSE, fill = NA) +
  scale_x_continuous(limits = c(quantile(rw$pH, probs = 0.01), 
                                quantile(rw$pH, probs = 0.95))) +
  scale_y_continuous(limits = c(quantile(rw$volatile.acidity, probs = 0.01), quantile(rw$volatile.acidity, probs = 0.95))) +
  scale_color_brewer(type = 'seq', guide = guide_legend(title = 'Quality')) +
  ggtitle("Wine Quality by pH vs volatile.acidity")

grid.arrange(mp3, ncol = 1)
```

Wines with low volatile.acidity are better quality wines.

```{r echo=FALSE, message=FALSE, warning=FALSE}
mp4 <- ggplot(data = rw, aes(x = alcohol, y = log10(sulphates), 
                             color = quality.factor)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = 'lm', se = FALSE, fill = NA) +
  scale_x_continuous(limits = c(quantile(rw$alcohol, probs = 0.01), 
                                quantile(rw$alcohol, probs = 0.99))) +
  scale_y_continuous(limits = c(quantile(log10(rw$sulphates), probs = 0.01), 
                                quantile(log10(rw$sulphates), probs = 0.95))) +
  scale_color_brewer(type = 'seq', guide = guide_legend(title = 'Quality')) +
  ggtitle("Wine Quality by alcohol vs log10 sulphates")

grid.arrange(mp4, ncol = 1)
```

High level of sulphates with higher alcohol are better wines.

```{r echo=FALSE, message=FALSE, warning=FALSE}
mp5 <- ggplot(data = rw, aes(x = alcohol, y = log10(chlorides), 
                             color = quality.factor)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = 'lm', se = FALSE, fill = NA) +
  scale_x_continuous(limits = c(quantile(rw$alcohol, probs = 0.01), 
                                quantile(rw$alcohol, probs = 0.99))) +
  scale_y_continuous(limits = c(quantile(log10(rw$chlorides), probs = 0.01), quantile(log10(rw$chlorides), probs = 0.95))) +
  scale_color_brewer(type = 'seq', guide = guide_legend(title = 'Quality')) +
  ggtitle("Wine Quality by alcohol vs log10 chlorides")

grid.arrange(mp5, ncol = 1)
```

chlorides does not have any effect on the wine quality.

```{r echo=FALSE, message=FALSE, warning=FALSE}
mp6 <- ggplot(data = rw, aes(x = log10(total.sulfur.dioxide), 
                             y = log10(free.sulfur.dioxide), 
                             color = quality.factor)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = 'lm', se = FALSE, fill = NA) +
  scale_x_continuous(limits = c(quantile(log10(rw$total.sulfur.dioxide), 
                                         probs = 0.01), 
                                quantile(log10(rw$total.sulfur.dioxide), 
                                         probs = 0.99))) +
  scale_y_continuous(limits = c(quantile(log10(rw$free.sulfur.dioxide), 
                                         probs = 0.01), 
                                quantile(log10(rw$free.sulfur.dioxide), 
                                         probs = 0.95))) +
  scale_color_brewer(type = 'seq', guide = guide_legend(title = 'Quality')) +
  ggtitle("Wine Quality by free.sulfur.dioxide vs total.sulfur.dioxide")

grid.arrange(mp6, ncol = 1)
```

free.sulfur.dioxide does not have any effect on the wine quality.


## Linear model for Quality

```{r echo=FALSE, message=FALSE, warning=FALSE}
m1 <- lm(quality ~ alcohol + citric.acid + sulphates + fixed.acidity, data = rw)
m2 <- update(m1, ~ . + volatile.acidity + pH + density)
m3 <- update(m2, ~ . + chlorides + free.sulfur.dioxide + residual.sugar 
             + total.sulfur.dioxide)

```

In model m1, I add those properties which seem to have positive strong 
correlation with wine quality. F-statistic comes out to be 159 
& R-squared is 0.2862. 

Next I add those variables which seem to have negative correlation 
with wine quality to m1.
F-statistic drops to 120 & R-squared improves to 0.345.
Here density and pH seems to loose the significance.

Next adding those properties which doesn't seem to have any effect on the 
wine quality.
F-statistic falls significantly to 81 and R-squared improved to 0.3606

But the p-value for all the 3 models doesn't change.


# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

Wines with High
1. alcohol
2. sulphates
3. fixed.acidity
4. citric.acid
are better quality wines.

But
1. free.sulfur.dioxide
2. chlorides
does not have any effect on the wine quality.

Low 
1. volatile.acidity
2. density
gives better rating for wines.

moderate pH seems to produce better wines.


### Were there any interesting or surprising interactions between features?

And decreasing the quantity of chlorides seemed to have better 
quality wines in boxplots.
But multivariate plots depicted that chlorides have no effect on the 
wine quality.

### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.

created 3 linear models for the dataset with 11 datapoints
1. alcohol + fixed.acidity + sulphates + citric.acid
2. alcohol + fixed.acidity + sulphates + citric.acid + volatile.acidity + pH
3. alcohol + fixed.acidity + sulphates + citric.acid + volatile.acidity + pH + 
residual.sugar + chlorides + free.sulfur.dioxide + total.sulfur.dioxide + 
density
 
Since he dataset has majority of the wines in medium group, there's very 
limited data for bad (1-4) and good (7-10) quality wines, it doesn't seem to 
predict properly. If we have more data for these quality wines then it would 
be a better predicting model.

------

# Final Plots and Summary

### Plot One
```{r echo=FALSE, message=FALSE, warning=FALSE, Plot_One}
mp1 <- ggplot(data = rw, aes(x = alcohol, y = citric.acid, 
                             color = quality.factor)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = 'lm', se = FALSE, fill = NA) +
  scale_x_continuous(limits = c(quantile(rw$alcohol, probs = 0.01), 
                                quantile(rw$alcohol, probs = 0.99))) +
  scale_y_continuous(limits = c(quantile(rw$citric.acid, 
                                         probs = 0.01), 
                                quantile(rw$citric.acid, 
                                         probs = 0.95))) +
  scale_color_brewer(palette = "Blues") +
  xlab('Alcohol [% by volume]') +
  ylab('Citric Acid [g / dm^3]') +
  ggtitle("Wine Quality by alcohol vs citric acid")

grid.arrange(mp1, ncol = 1)
```

### Description One
This Chart clearly depicts that wines with high citric.acid & high alcohol 
wines are better wines.

### Plot Two
```{r echo=FALSE, message=FALSE, warning=FALSE, Plot_Two}
mp4 <- ggplot(data = rw, aes(x = alcohol, y = log10(sulphates), 
                             color = quality.factor)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = 'lm', se = FALSE, fill = NA) +
  scale_x_continuous(limits = c(quantile(rw$alcohol, probs = 0.01), 
                                quantile(rw$alcohol, probs = 0.99))) +
  scale_y_continuous(limits = c(quantile(log10(rw$sulphates), probs = 0.01), 
                                quantile(log10(rw$sulphates), probs = 0.95))) +
  scale_color_brewer(type = 'seq', guide = guide_legend(title = 'Quality')) +
  xlab('Alcohol [% by volume]') +
  ylab('Sulphates [potassium sulphate - g / dm3]') +
  ggtitle("Wine Quality by alcohol vs log10 sulphates")

grid.arrange(mp4, ncol = 1)
```

### Description Two
This plot clearly depicts high alcohol levels and high sulphates levels produce 
better quality wines.

### Plot Three
```{r echo=FALSE, message=FALSE, warning=FALSE, Plot_Three}
mp3 <- ggplot(data = rw, aes(x = pH, y = volatile.acidity, 
                             color = quality.factor)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = 'lm', se = FALSE, fill = NA) +
  scale_x_continuous(limits = c(quantile(rw$pH, probs = 0.01), 
                                quantile(rw$pH, probs = 0.95))) +
  scale_y_continuous(limits = c(quantile(rw$volatile.acidity, probs = 0.01), quantile(rw$volatile.acidity, probs = 0.95))) +
  scale_color_brewer(type = 'seq', guide = guide_legend(title = 'Quality')) +
  xlab('pH') +
ylab('Volatile Acidity [Aceti Acid - g / dm^3]') +
  ggtitle("Wine Quality by pH vs volatile.acidity")

grid.arrange(mp3, ncol = 1)
```

### Description Three
Wines with low volatile acidity combined with moderate pH values are better wines.

------

# Reflection
1. High Alcohol content, is important for better wine qulaity ratings.
2. High Sulphates are the next important property for better quality wines.
3. Increased citric.acid & fixed.acidity have positive correlation with wine 
quality.
4. Moderate pH levels are better quality wines.
5. Density, chlorides, residual.sugar, free.sulfur.dioxide & 
total.sulfur.dioxide doesn't seem to have big effect on the wine qulaity.
6. Low volatile.acidity seems to have positive effect on wine quality.

Since the dataset is limited to the majority of the medium quality wines, 
it was hard to depict what properties would have played important role in 
determining the quality of the red wine.

When fitted linear model with all the variables, citric.acid and fixed.acidity 
lost the significance but for other 2 linear models m1 & m2, these are important 
properties to consider.

In linear model m3, about 35% of the variance in quality of wine is explained by 
all the properties of the wine in dataset.
If we have more data on the extreme quality wines bad, good than we predict a 
better linear model. And some other sophisticated models can be used 
to better understand what chemical properties make a wine better quality wines.
